\documentclass{article}


\title{Before The Crash}
\author{@Scruffwuffulous}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{libertine}
\usepackage[most]{tcolorbox}
\usepackage{hyperref}
\usepackage{hyperref-patches}

\newenvironment{info}[1]{
    \begin{tcolorbox}[
        colback=blue!5!white,
        colframe=blue!35!black,
        title=#1,
        arc=1mm,
        enhanced,
        drop shadow
        ]
    }{
    \end{tcolorbox}
}

\newenvironment{Theo}{begin_def}{end_def}

\begin{document}


\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
\definecolor{arsenic}{rgb}{0.23, 0.27, 0.29}
\pagecolor{aliceblue}
\color{arsenic}


\maketitle
\pagebreak

\tableofcontents
\pagebreak

\section{Ideas Section (to be removed before any publishing)}

What do we need to get across?
\begin{itemize}
    \item Two important questions that the player and the characters should explore
    \subitem Who am I really / What am I and why?
    \subitem How do I fit into this society and world in which I find myself
    \item It needs to give the vibes of a cyberpunk setting in flavour as well
\end{itemize}
What do we want to use?
\begin{itemize}
    \item Aim to use a hack of the Cortex Prime system
    \subitem because I love the central dice mechanics
    \subitem This requires a choice of the prime sets
    \item We want to create the vibes of a Vangelis score mixed with some high-octane punk rock
    \subitem Ideally we want to have a healthy balance of decent character moments amidst the fun of bashing those corpo bastards.
    \item We need to decide on the nature of the setting:
    \subitem Are there synths/replicants/whatever?
    \subitem Are there augs/mods/chrome?
    \subitem How much control over their life does the average person have?
    \subitem And who really holds that power?
\end{itemize}
Finally, how do we want to present this to players, GMs, and anyone else who happens across this document?
\begin{itemize}
    \item Sections should start with an Intro
    \subitem First is probably an intro to RPGs (or at least my perspective on them)
    \subitem This should have a basic setting primer
    \subitem Then probably a quick example of the basics of the dice system
    \subitem To finish the Introduction, we should do an intro to the book and how to use it
    \item Now we need a section on characters and how to build them, just the basics and reference stuff
    \item Next should be a selection which contains \textbf{all} the details on how to resolve any rules disparity
    \item Now, the last things that a player needs to know before they tap out. i.e. a section on the given worldbuilding, and a note to say you may want to make your own...
    \item So begins the GM section (I need a funny thing for GM to stand for) To start we need to do a GM intro
    \item Then a quick breakdown on how to structure a session
    \item Now how to structure a campaign or any extended story
    \item A bit on how to generate GMPCs or NPCs whatever you want to call them
    \item A treatise on what Cyberpunk is to me, and what it can be to you...
    \item Then comes some kind of index, this is going to be fun...
\end{itemize}

When \textit{ALL OF THIS} is done, we can consider fixing up a nicer visual style

\section{Scratchpad}

OH MY GOD WHYYYYYY

Some notes I must transfer from paper, which all seem to be setting based?:

\begin{enumerate}
    \item AI never succeeded :/ Besides: it's cheaper to rip the consciousness of debtors and old creatives...
    \item Body modification has become cheap \& stylish. Good body modification is just stylish...
    \item Cyberspace is on its third great instance \& is almost indistinguishable from a dark mirror of reality. Those who control it wield great powers
    \item Everyone can interface with almost anything or anyone...
    \item Who owns you?
\end{enumerate}

Additionally (more mechanically focussed) I wrote:
\begin{itemize}
    \item One of the Prime Sets is "Memories (of People?)"
\end{itemize}

Other additional stuff:

\begin{itemize}
    \item No hack skill, no persuade skill
\end{itemize}

\include{SectionExample}

\end{document}