\section{Ideas Section (to be removed before any publishing)}

What do we need to get across?
\begin{itemize}
    \item Two important questions that the player and the characters should explore
    \subitem Who am I really / What am I and why?
    \subitem How do I fit into this society and world in which I find myself
    \item It needs to give the vibes of a cyberpunk setting in flavour as well
\end{itemize}
What do we want to use?
\begin{itemize}
    \item Aim to use a hack of the Cortex Prime system
    \subitem because I love the central dice mechanics
    \subitem This requires a choice of the prime sets
    \item We want to create the vibes of a Vangelis score mixed with some high-octane punk rock
    \subitem Ideally we want to have a healthy balance of decent character moments amidst the fun of bashing those corpo bastards.
    \item We need to decide on the nature of the setting:
    \subitem Are there synths/replicants/whatever?
    \subitem Are there augs/mods/chrome?
    \subitem How much control over their life does the average person have?
    \subitem And who really holds that power?
\end{itemize}
Finally, how do we want to present this to players, GMs, and anyone else who happens across this document?
\begin{itemize}
    \item Sections should start with an Intro
    \subitem First is probably an intro to RPGs (or at least my perspective on them)
    \subitem This should have a basic setting primer
    \subitem Then probably a quick example of the basics of the dice system
    \subitem To finish the Introduction, we should do an intro to the book and how to use it
    \item Now we need a section on characters and how to build them, just the basics and reference stuff
    \item Next should be a selection which contains \textbf{all} the details on how to resolve any rules disparity
    \item Now, the last things that a player needs to know before they tap out. i.e. a section on the given worldbuilding, and a note to say you may want to make your own...
    \item So begins the GM section (I need a funny thing for GM to stand for) To start we need to do a GM intro
    \item Then a quick breakdown on how to structure a session
    \item Now how to structure a campaign or any extended story
    \item A bit on how to generate GMPCs or NPCs whatever you want to call them
    \item A treatise on what Cyberpunk is to me, and what it can be to you (Wires and Chains...)
    \item Welcome the players back to end with an extended example of play, using the characters established earlier in the Characters chapter
    \item Then comes some kind of index, this is going to be fun...
\end{itemize}

When \textit{ALL OF THIS} is done, we can consider fixing up a nicer visual style

Current choice of attributes and the like:

Prime Sets:
\begin{itemize}
    \item Distinctions
    \subitem These are just 3 d8-rated descriptors of your character that come with a bonus SFX
    \item Roles
    \subitem These should be split into classes of roles, pick one from each, then one more.
    \subitem Needs more thought, split Detective, Corporate, etc.?
    \item Relationships
    \subitem Meant to incentivise players to create backstory elements on the fly
\end{itemize}

Non-Prime Sets: (these are all maybes)
\begin{itemize}
    \item Affiliations
    \subitem These can just become assets
    \item Powers
    \subitem These can become assets and SFX
    \item Resources (rework like FATE)
    \subitem These can become assets
    \item Signature Assets (this is a definite)
    \subitem These should be essential to character creation
    \item Skills \& Specialities
    \subitem I like specialities, but perhaps they can be worked into Roles? Skills, no
    \item Values
    \subitem Tempting, we shall see...
\end{itemize}
